Binning Strategies and Related Loss for Large Data

### 2015-05-12 Paper.Rnw
space?

Figure~\ref{freqbinning} shows binned scatterplots for the simulated normal data with quantile frequency binning and standard log frequency binning. \ktm{Both shading schemes are effective at reducing the visual impact of the highest density at the center, allowing for the differences in the surrounding bin frequencies to be emphasized. It should be noted that the frequency binning algorithm produced binned scatterplots that visually very similar, but this will not always be the case. It occured in this scenario because the distribution of log bin frequencies from the bivariate normal data is nearly uniform, thus the standard log binning aligns closely with the quantile binning.}

>>>>

Figure~\ref{freqbinning} shows binned scatterplots for the simulated normal data with quantile frequency binning and standard log frequency binning. \ktm{Both shading schemes are effective at reducing the visual impact of the highest density at the center, allowing for the differences in the surrounding bin frequencies to be emphasized. It should be noted that the frequency binning algorithm produced binned scatterplots that visually very similar, but this will not always be the case. It occurred in this scenario because the distribution of log bin frequencies from the bivariate normal data is nearly uniform, thus the standard log binning aligns closely with the quantile binning.}
